R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
add example and python blurb

@@

- Code chunk options
- Knit options
- URLs and internal links
- Table of Contents
- Table Output
- RStudio documentation, etc

@@

>>>>

Let us imagine that we are beginning a project where we explore the classic
[`iris` dataset](todo). We might approach the problem by first specifying the
`iris` dataset as our only input. To ensure auditability and reproducibility, I
might save and [open source the dataset](todo) as well as specify it as a parameter
for my research in the YAML header.

```
---
title: "Iris Research"
author: "Cole Arendt"
date: "1/6/2019"
output: pdf_document
params:
  input_data: "iris.rds"
---
```

Now, I need R packages to make my work more efficient. I have chosen `dplyr`,
`tidyr`, and `ggplot2`. Though I reference these packages in my code, I should
also keep track of which versions of the package I am using. For this task, I
might use `packrat::.snapshotImpl(".", snapshot.sources = FALSE)`.

Finally, we come to my actual research. As I explore this dataset, I must ensure
that my results are programmatic. This means plots, values, and prose should
be dependent only on my input dataset.

When complete, I will be able to generate my research paper with one line of
code (or one click):

```r
rmarkdown::render("./ex/ex-research.Rmd")
```

If I received updated, corrected, or otherwise different data (i.e. "iris_altered.rds"),
changing my single input parameter and re-rendering the report will reliably rebuild my
analysis off of different data. Further, any other researcher can take my document and R
packages to reproduce or validate my results. Feel free to give it a shot yourself!

@@

## CODE CHUNK OPTIONS

Every code chunk has _many_ options. These are specified

## KNIT OPTIONS

## URLS AND INTERNAL LINKS

## TABLE OF CONTENTS

## TABLE OUTPUT

## RSTUDIO DOCUMENTATION

@@

Python is a general purpose programming language that is increasingly
common in data science. It has great utility in many regards and many
useful modules (akin to packages) that can be useful to a researcher.

R Markdown, despite its name, is actually remarkably language agnostic. You
can include code chunks in other languages (like Python, bash, Stan, and SQL) in
your R Markdown documents.

Python, in particular, has recently improved support in R Markdown and the RStudio IDE.
Specifically, the [`reticulate`](todo) package makes it possible to specify the python
version and conda / virtual environment, as well as persist objects across code chunks. 
There is also native support for including python plots and other output in your
rendered R Markdown document. There is much written already about this work flow. If
interested, the following articles are helpful:

- todo
- todo
